INSTRUCTION SETS FOR STRANGERS

### 2021-09-29 instructionsetsforstrangers/instructionsetsforstrangers.tex
updated index
some instruatcion sets updates

\title{INSTRUCTION SETS FOR STRANGERS}
\date{}
\author{Lauria Clarke}

@@

\clearpage
\section*{PART II - Iteration}
\subsection*{prototyping}

@@

>>>>

\title{INSTRUCTION SETS FOR STRANGERS}
\date{\today}
\author{Lauria Clarke}

@@

\clearpage
\section*{PART II - Iteration}
\subsection*{initial prototypes}

@@

\clearpage
\subsection*{final prototype}

Combinging the feedback from class critique we needed to move forward on the three main areas of improvemnet:
\begin{itemize}
\item
  make the entire mechanism more robust for installation
\item
  make the hand and activation mechnaism more visible at night
\item
  change the activation mechnaism so that it is easier to understand how to activate the hand
\end{itemize}

First we decided to increase the scale of the wave machine and make it more robust. After a quick survey of the scrap bin in the wood shop we found all the materials that we needed. The first step was making the hands themselves. These were cut from two sheets of $1/16$ inch plywood on the bandsaw.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth, angle=270]{"images/III/plainhands.jpg"}
\caption{Big hands!}
\end{figure}

Next we found some $1/8$ inch and $3/4$ inch plywood and created the base of the new mechanishm. At this point we also determined the best way to make the handle to activate the hand waving easier to use. A handle that needs to be pulled is ambiguous and not very visual, so we decided to make the handle another lever in the shape of a hand that would encourage users to use their hands to activate it. This was a simple lever that sticks out of one side of the mechanism pulled one side of the hand waving lever down when activated. \href{https://drive.google.com/file/d/1A4jMRefTUcI-PZPhbS6XSqFU6V4kzS8j/view?usp=sharing}{Link to video of lever action.}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth, angle=270]{"images/III/leverwithbase.jpg"}
\caption{Big hands!}
\end{figure}
